Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Aceptado otro cambio de @fergunet

There are some other components, namely: the \textit{Security Policies/Risk Management} tool, that lets the company's chief security officer (CSO) to define and manage Security Policies and Rules in a friendly way. It also lets the management of risk-related information, useful for the RT2AE process, such as the assets' values. The \textit{Privacy Enhancing System} which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system. The \textit{User, Context, Event Data Receiver} is devoted to receive data from the device side (events, user-related, etc.) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task). Finally, there is another \textit{Connection Manager} which controls the communication with the device side. %FERGU: no usar etc en artículos, mejor poner: (events, user-related LOQUESEA, among others)

>>>>

There are some other components, namely: the \textit{Security Policies/Risk Management} tool, that lets the company's chief security officer (CSO) to define and manage Security Policies and Rules in a friendly way. It also lets the management of risk-related information, useful for the RT2AE process, such as the assets' values. The \textit{Privacy Enhancing System} which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system. The \textit{User, Context, Event Data Receiver} is devoted to receive data from the device side (events, or user-related data, among others) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task). Finally, there is another \textit{Connection Manager} which controls the communication with the device side. %FERGU: no usar etc en artículos, mejor poner: (events, user-related LOQUESEA, among others)
% Cambiado
